I thank my adviser, Evan Skillman, for all of his time and effort spent guiding
me to my PhD. He has provided me with many wonderful opportunities that have
truly enriched my graduate school experience. I've met great people, traveled
to exciting places, and worked on interesting projects all because of him, and
I cannot imagine how my trajectory would be different had he not accepted me as
a student so many years ago. He always has great advice, both academic and on
life. Without the latter, this dissertation may never have been written. Above
all, Evan is a patient and understanding person, and it has been a pleasure
working for him. Plus, he's a riot at dinner.

I must also thank my graduate comrades, both those who are sill toiling away
and those who have moved on to better things. Graduate school is not for the
faint of heart and there were times when I felt like quitting. The friends I've
made over the years have been vital for balancing the bad with the good, and
have made this whole experience worth something more than just attaining a
degree.

For my parents, words simply cannot express my love and gratitude. While I was
growing up, Mom and Dad both taught me the importance of education and it was
always clear that I would one day go to college. However, I never felt
pressured to pursue any given profession. They allowed me to discover myself on
my own terms and actively fostered my interests, even when my interests were
borderline ridiculous. (Remember when I thought I wanted to be a rockstar?) As
for most young adults, life got hard when I started college, and even more so
when I started graduate school. There is only so much I can do on my own, and
my parents have helped me out on countless occasions along the way, allowing me
to focus on my studies. The only reason I've made it this far is with their
constant, unconditional support.

I give my most heartfelt thanks to my wife, Annie, who, for better or worse,
has stuck with me on this trying journey through graduate school. I remember
when we both started our professional studies at the University of Minnesota.
We were mostly care-free and couldn't have been happier chasing our ultimate
academic goals. We had no idea what challenges were ahead of us. The hours
slowly grew longer, the dinners less frequent, and the stress became heavy. I
even got my first gray hairs. And Annie has been there for me through all of
it. She always made me feel better after a bad exam and shared my joy in my
successes, and she is still the person I most look forward to seeing at the end
of the day (and I miss her when I don't). She always inspired me to keep going
and provided words of encouragement when I needed it -- except when she didn't.
After all, she has never been afraid to force me to think about what I really
want in life and sometimes that meant having difficult conversations. Deep down
she's a pragmatist and I like her for that, too, because she makes me a better
person. We've been through so much together and finally earning my degree is as
much her victory as it is mine. She is my equal, my best friend, and the love
of my life.
