\chapter{Introduction}
\label{introduction}

%\section{Stellar population modeling}
%
%SSP modeling requires stellar evolution models, stellar spectral libraries, and
%IMF; all of these (except the IMF, if it's universal) depend on metallicity.
%
%SPS codes are typically based on one dimensional models, but processes like
%convection, rotation, mass-loss, close binary interactions, and thermal
%pulsation are inherently three dimensional.
%
%Core and envelope ``overshooting'' refers to in increase in size of a
%convective layer relative to a more classical radiative-convective boundary.
%The amount of overshooting is essentially a free parameter that is tuned by
%observations.
%
%SPS codes typically do not include binary evolution.
%
%Input models are not usually completely theoretical, but rather
%``semi-empirical'' such that the physics of the models are tuned using
%observations. For example, the TP-AGB component of the Padova isochrones
%\citep{Marigo:2008} was calibrated using observations of nearby galaxies
%\citep{Girardi:2010}.




\section{Evaluating ultraviolet flux as a star formation tracer on sub-kpc scales}

A common technique for estimating global star formation rates (SFRs) in
individual galaxies is to measure the total flux at wavelengths known to trace
recent star formation (SF), such as ultraviolet (UV) emission from
intermediate- and high-mass stars. After correcting for dust extinction, an
observed flux can be converted into a SFR using a suitable calibration, which
is typically a linear scaling of intrinsic luminosity derived from population
synthesis modeling. The modeling process requires a set of stellar evolution
models and a stellar initial mass function (IMF), as well as a characterization
of the star formation history (SFH; the evolution of SFR over time) and the
metallicity of the population. These quantities are often not well-constrained
for a given system and need to be assumed (see reviews by
\citealt{Kennicutt:1998}, \citealt{Kennicutt:2012}, and references therein).

A set of flux calibrations widely used in extragalactic studies were presented
by \citet[][see \citealp{Kennicutt:2012} for updates]{Kennicutt:1998}. These
calibrations are based on models of a generic population with solar
metallicity, a fully populated IMF, and a SFR that has been constant over the
lifetime of the tracer emission ($\sim 100\myr$ for UV). The flux calibrations
are therefore applicable to any population that can be assumed to approximate
the generic population, such as spiral galaxies. In environments with low total
SF (i.e., low mass) or on subgalactic scales, however, the assumptions of a
fully populated IMF and a constant SFR start to become tenuous. As a result,
applying the flux calibrations in these situations can lead to inaccurate SFR
estimates.

For populations located within a few Mpc, it is possible to measure SFRs more
directly by fitting the color magnitude diagram (CMD) of the resolved stars to
obtain a SFH \citep{Dolphin:2002}. At its core, CMD fitting is a population
synthesis technique just like flux calibration (albeit much more complex) and
thus requires a set of stellar evolution models, an IMF, and an accounting of
dust. The primary advantage of CMD fitting over the flux calibration method for
obtaining SFRs, however, is the elimination of assumptions about the SFH and
metallicity. CMD-based SFHs thus provide a relative standard for testing the
accuracy of SFR estimates from commonly used flux calibrations, especially in
applications where the underlying full-IMF and constant-SFR assumptions are not
strictly satisfied. More generally, the SFHs can be used to test results from
any other flux-based method, such as ages and masses derived under the simple
stellar population (SSP) assumption.

With recent Hubble Space Telescope (HST) observations from the Panchromatic
Hubble Andromeda Treasury \citep[PHAT;][]{Dalcanton:2012}, we have measured the
recent SFHs ($< 500\myr$) of 33 UV-bright regions in M31 and compared
them with SFRs derived from UV flux. We also compared the SFHs with ages and
masses derived from UV flux by treating the regions as SSPs. The UV-bright
regions were cataloged by \citet[][\citetalias{Kang:2009} hereafter]{Kang:2009} using
Galaxy Evolution Explorer (GALEX) far-UV (\fuv{}, $\lambda \sim
1540\ang$) flux and have areas ranging from $10^4$ to
$10^6\pc^2$. This range of sizes allowed us to test the reliability
of the full-IMF, constant-SFR, and SSP assumptions on sub-kpc scales.




\section{From sub-kpc to galactic-scales: evaluating ultraviolet flux using
synthetic ultraviolet flux maps of M31}

M31 is a well-studied, $\sim L_\ast$ galaxy and has been observed at a variety
of wavelengths, e.g., in the ultraviolet (UV) by the Galaxy Evolution Explorer
\citep[GALEX;][]{Morrissey:2007}, in the optical, including H$\alpha$, for the
Local Group Galaxies Survey \citep{Massey:2006}, and in the infrared by the
Spitzer Space Telescope \citep{Gordon:2006}. The wealth of high-quality data
available for M31 provides a valuable opportunity to model various observations
and test our current understanding of stellar astrophysics. In particular, the
initial mass function (IMF), stellar evolution and spectra models, and
extinction curves are all required to model the light produced by a galaxy.

A critical ingredient for modeling the flux from a galaxy is a detailed
knowledge of its underlying SFH. Deriving SFHs by CMD analysis is a reliable
method that can be used whenever photometry of resolved stars is available. An
extensive optical photometric catalog for M31 has been compiled by PHAT
\citep{Dalcanton:2012}, and \citet{Lewis:2014} have used these data to derive
the spatially-resolved SFH of the northeast quadrant. With sub-kpc resolution,
this SFH dataset is the ideal input for stellar population synthesis codes that
model total flux given a population's SFR and metallicity evolution. The result
is a set of spatially-resolved maps of synthetic broadband flux in M31 which
can be compared with observations.

The \citet{Lewis:2014} SFHs can also be used to create temporally-averaged SFR
maps. Because the SFHs were derived from the resolved stars without any prior
assumptions about the SFHs, such maps provide a standard against which
flux-based SFR estimates \citep[e.g., using any of the calibrations
from][]{Kennicutt:2012} can be tested. Using integrated flux to estimate SFRs
for distant galaxies, where resolved stars are not available, is a common
technique in extragalactic astronomy. Previous studies have investigated how
flux-based SFR estimators hold up against resolved-star SFHs in sub-kpc
UV-bright regions \citep{Simones:2014} and in low-metallicity dwarf galaxies
\citep{McQuinn:2014}. The SFHs of \citet{Lewis:2014} based on data from PHAT
make it possible to broaden this type of analysis to include a wide variety of
environments in the most prominent local group spiral galaxy.

In this study, we have used the PHAT CMD-based SFHs and stellar population
synthesis to create maps of synthetic ultraviolet (UV) flux at sub-kpc
resolution for the northeast quadrant of M31. We then compared the synthetic
flux maps with observations from GALEX. We have only focused on GALEX \fuv{}
and \nuv{} (far and near UV), though this work can easily be extended to other
wavelength regimes. In \S \ref{mfx:syntheticfluxmaps}, we describe the SFH
dataset and the production of the synthetic flux maps. \S
\ref{mfx:observations} describes the process of producing observed flux maps
from GALEX \fuv{} and \nuv{} images. The creation of SFR maps both from the
SFHs and the observed fluxes using common flux-SFR calibrations are described
in \S \ref{mfx:sfrestimates}. In \S \ref{mfx:discussion}, we compare the
synthetic maps with the observations and compare mean SFR maps with SFRs
estimated from observed flux. We conclude in \S \ref{mfx:conclusion}.
